---
title: "HBGDki adjustment DAGs"
author: "Andrew Mertens"
date: "July 10, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# A single DAG for all risk factors involves making too many assumptions about the direction of covariate relationship, so we create a DAG per risk factor. For example, does low maternal education lead to lower household wealth, or does household wealth lead to lower maternal education opportunities? When analyzing the association between maternal education and stunting, we assume household wealth is a confounder rather than on the causal path, and adjust for it, and vice versa. However, even when elimating all bi-directional edges for each DAG, making sure that only the variables that are clearly on the causal pathway are not controlled for, the DAGs are complicated and sometimes un-identifiable. In these cases, all direct parents of the risk factor and outcome are chosen as the adjustment set.
# 
# Can you check behind me and make sure A) I'm not including any variables on the causal pathway in the adjustment set for each risk factor, and B) I'm nt excluding any important confounders from each adjustment set?
# 
# There are three parts to this document. 1) a table of the variable name codes and a description of each variable. 2) A list of each risk factor and the corresponding adjustment set, and 3) a DAG for each risk factor, with the title noting either the adjustment set for estimating the risk factor - stunting association, or marked as non-identifiable if there is no way to block the backdoor paths. At this point, I haven't figured out an easy way to identify the backdoor paths using the daggity R package in these complex DAGs, so I choose all parents of the risk factor as the adjustment set.

```


## DAGs specific to each risk factor

A single DAG for all risk factors involves making too many assumptions about the direction of covariate relationship, so we create a DAG per risk factor. For example, does low maternal education lead to lower household wealth, or does household wealth lead to lower maternal education opportunities? When analyzing the association between maternal education and stunting, we assume household wealth is a confounder rather than on the causal path, and adjust for it, and vice versa. However, even when elimating all bi-directional edges for each DAG, making sure that only the variables that are clearly on the causal pathway are not controlled for, the DAGs are complicated and sometimes un-identifiable. In these cases, all direct parents of the risk factor and outcome are chosen as the adjustment set.

There are three parts to this document. 1) a table of the variable name codes and a description of each variable. 2) A list of each risk factor and the corresponding adjustment set, and 3) a DAG for each risk factor, with the title noting either the adjustment set for estimating the risk factor - stunting association, or marked as non-identifiable if there is no way to block the backdoor paths. At this point, I haven't figured out an easy way to identify the backdoor paths using the daggity R package in these complex DAGs, so I choose all parents of the risk factor as the adjustment set.




## List of adjustment covariates for each risk factor



```{r, include=F}


library(dagitty)
library(lavaan)
library(ggdag)
library(stringr)
library(knitr)



all_exposures = c("sex", "month", "mage",   "fage",  "meducyrs",  "feducyrs", "single", 
  "hhwealth","hfoodsec",
  "mhtcm", "fhtcm","mwtkg",  "mbmi", "arm", "hdlvry", 
  "vagbrth", "birthwt",  "birthlen",  "gagebrth", 
  "brthordr",  "brthmon", "earlybf",
"nchldlt5", "nhh", "nrooms",
"impsan",  "safeh2o",   "trth2o",  "cleanck",  "impfloor", "enstunt","BF_practice", "diarrhea")


var_labels = c("Child gender", "Month of measurement", "Mother's age",   "Father's age",  "Mother's education",  "Father's education", "Widowed/divorced/seperated/single parent", 
  "Asset-based ousehold wealth quartile","Household food security category",
  "Mother's height", "Father's height","Mother's weight",  "Mother's MBI", "Intervention arm", "Child delivered at home/hospital", 
  "Vaginal birth", "Birth weight",  "Birth length",  "Gestational age at birth",
  "First/second/thirdborn+ child",  "Birth month", "Breastfed within an hour of birth",
"Number of children <5 in house", "Number of people in house", "Number of rooms in house",
"Improved sanitation",  "Safe water source",   "Treats drinking water",  "Clean cooking fuel",  
"Improved floor", "Enrolled stunted","Exclusive or predominant breastfeeding under 6 months", "Percent days with diarrhea")
```

```{r, echo=F}

knitr::kable(data.frame(Variable_Name=all_exposures, Description=var_labels))
```


```{r, include=F}


d <-paste0("dag {",


#---------------------------------
#Variables affecting the outcome
#---------------------------------

"
mage -> Y_Stunted    
fage -> Y_Stunted           
mhtcm -> Y_Stunted    
fhtcm -> Y_Stunted
mwtkg -> Y_Stunted    
mbmi -> Y_Stunted    
single -> Y_Stunted
meducyrs -> Y_Stunted 
feducyrs -> Y_Stunted

birthwt -> Y_Stunted  
birthlen -> Y_Stunted 
gagebrth -> Y_Stunted 
vagbrth -> Y_Stunted  
hdlvry -> Y_Stunted

sex -> Y_Stunted 
brthordr -> Y_Stunted  
brthmon -> Y_Stunted 

impsan -> Y_Stunted 
safeh2o -> Y_Stunted  
trth2o -> Y_Stunted   
cleanck -> Y_Stunted  
impfloor -> Y_Stunted 

nchldlt5 -> Y_Stunted
nhh -> Y_Stunted
nrooms -> Y_Stunted

diarrhea -> Y_Stunted

BF_practice -> Y_Stunted

hfoodsec -> Y_Stunted
hhwealth -> Y_Stunted
enstunt -> Y_Stunted
earlybf -> Y_Stunted

arm -> Y_Stunted
month -> Y_Stunted     
",

#---------------------------------
#Variables affecting other variables
#---------------------------------


#Parental_Vars: parental characteristics
  #Variables affecting: mage 
  "
fage -> mage           
mhtcm -> mage    
fhtcm -> mage
mwtkg -> mage    
mbmi -> mage    
single -> mage
meducyrs -> mage 
feducyrs -> mage

brthordr -> mage  

impsan -> mage 
safeh2o -> mage  
trth2o -> mage   
cleanck -> mage  
impfloor -> mage 

nchldlt5 -> mage
nhh -> mage
nrooms -> mage

hfoodsec -> mage
hhwealth -> mage 

arm -> mage
month -> mage
  ",   
  #Variables affecting: fage
  "
mage -> fage           
mhtcm -> fage    
fhtcm -> fage
mwtkg -> fage    
mbmi -> fage    
single -> fage
meducyrs -> fage 
feducyrs -> fage

brthordr -> fage  

impsan -> fage 
safeh2o -> fage  
trth2o -> fage   
cleanck -> fage  
impfloor -> fage 

nchldlt5 -> fage
nhh -> fage
nrooms -> fage

hfoodsec -> fage
hhwealth -> fage 

arm -> fage
month -> fage

  ",           
  #Variables affecting: mhtcm
  "
mage -> mhtcm    
fage -> mhtcm           
fhtcm -> mhtcm
mwtkg -> mhtcm    

single -> mhtcm
meducyrs -> mhtcm 
feducyrs -> mhtcm

impsan -> mhtcm 
safeh2o -> mhtcm  
trth2o -> mhtcm   
cleanck -> mhtcm  
impfloor -> mhtcm 

nchldlt5 -> mhtcm
nhh -> mhtcm
nrooms -> mhtcm

hfoodsec -> mhtcm
hhwealth -> mhtcm

arm -> mhtcm
month -> mhtcm

  ",    
  #Variables affecting: fhtcm
  "
mage -> fhtcm    
fage -> fhtcm           
mhtcm -> fhtcm
mwtkg -> fhtcm    

single -> fhtcm
meducyrs -> fhtcm 
feducyrs -> fhtcm

impsan -> fhtcm 
safeh2o -> fhtcm  
trth2o -> fhtcm   
cleanck -> fhtcm  
impfloor -> fhtcm 

nchldlt5 -> fhtcm
nhh -> fhtcm
nrooms -> fhtcm

hfoodsec -> fhtcm
hhwealth -> fhtcm

arm -> fhtcm
month -> fhtcm

  ",
  #Variables affecting: mwtkg
  "
mage -> mwtkg    
fage -> mwtkg           
mhtcm -> mwtkg
fhtcm -> mwtkg    

single -> mwtkg
meducyrs -> mwtkg 
feducyrs -> mwtkg

impsan -> mwtkg 
safeh2o -> mwtkg  
trth2o -> mwtkg   
cleanck -> mwtkg  
impfloor -> mwtkg 

nchldlt5 -> mwtkg
nhh -> mwtkg
nrooms -> mwtkg

hfoodsec -> mwtkg
hhwealth -> mwtkg

arm -> mwtkg
month -> mwtkg

  ",    
  #Variables affecting: mbmi
  "
mage -> mbmi    
fage -> mbmi           
single -> mbmi
meducyrs -> mbmi 
feducyrs -> mbmi
fhtcm -> mbmi    

impsan -> mbmi 
safeh2o -> mbmi  
trth2o -> mbmi   
cleanck -> mbmi  
impfloor -> mbmi 

nchldlt5 -> mbmi
nhh -> mbmi
nrooms -> mbmi

hfoodsec -> mbmi
hhwealth -> mbmi

arm -> mbmi
month -> mbmi

  ",    
  #Variables affecting: single
  "
mage -> single    
fage -> single           
mhtcm -> single    
fhtcm -> single
mwtkg -> single    
mbmi -> single    
meducyrs -> single 
feducyrs -> single

impsan -> single 
safeh2o -> single  
trth2o -> single   
cleanck -> single  
impfloor -> single 

nchldlt5 -> single
nhh -> single
nrooms -> single

hfoodsec -> single
hhwealth -> single

arm -> single
month -> single


  ",
  #Variables affecting: meducyrs
  "
mage -> meducyrs    
fage -> meducyrs           
mhtcm -> meducyrs    
fhtcm -> meducyrs
mwtkg -> meducyrs    
mbmi -> meducyrs    
single -> meducyrs
feducyrs -> meducyrs

impsan -> meducyrs 
safeh2o -> meducyrs  
cleanck -> meducyrs  
impfloor -> meducyrs 

nchldlt5 -> meducyrs
nhh -> meducyrs
nrooms -> meducyrs

hfoodsec -> meducyrs
hhwealth -> meducyrs

arm -> meducyrs
month -> meducyrs

  ",
  #Variables affecting: feducyrs
  "
mage -> feducyrs    
fage -> feducyrs           
mhtcm -> feducyrs    
fhtcm -> feducyrs
mwtkg -> feducyrs    
mbmi -> feducyrs    
single -> feducyrs
meducyrs -> feducyrs

impsan -> feducyrs 
safeh2o -> feducyrs  
cleanck -> feducyrs  
impfloor -> feducyrs 

nchldlt5 -> feducyrs
nhh -> feducyrs
nrooms -> feducyrs

hfoodsec -> feducyrs
hhwealth -> feducyrs  

arm -> feducyrs
month -> feducyrs

",

#Birth_Antho: birth anthropometry/modifiable birth characteristics
  #Variables affecting: birthwt 
  "   
mage -> birthwt    
fage -> birthwt           
mhtcm -> birthwt    
fhtcm -> birthwt
mwtkg -> birthwt    
mbmi -> birthwt    
single -> birthwt
meducyrs -> birthwt 
feducyrs -> birthwt

birthlen -> birthwt 

vagbrth -> birthwt  
hdlvry -> birthwt

sex -> birthwt 
brthordr -> birthwt  
brthmon -> birthwt 

impsan -> birthwt 
safeh2o -> birthwt  
trth2o -> birthwt   
cleanck -> birthwt  
impfloor -> birthwt 

nchldlt5 -> birthwt
nhh -> birthwt
nrooms -> birthwt

hfoodsec -> birthwt
hhwealth -> birthwt

arm -> birthwt
month -> birthwt

  ", 
  #Variables affecting: birthlen 
  "
mage -> birthlen    
fage -> birthlen           
mhtcm -> birthlen    
fhtcm -> birthlen
mwtkg -> birthlen    
mbmi -> birthlen    
single -> birthlen
meducyrs -> birthlen 
feducyrs -> birthlen

birthwt -> birthlen 

vagbrth -> birthlen  
hdlvry -> birthlen

sex -> birthlen 
brthordr -> birthlen  
brthmon -> birthlen 

impsan -> birthlen 
safeh2o -> birthlen  
trth2o -> birthlen   
cleanck -> birthlen  
impfloor -> birthlen 

nchldlt5 -> birthlen
nhh -> birthlen
nrooms -> birthlen

hfoodsec -> birthlen
hhwealth -> birthlen

arm -> birthlen
month -> birthlen


  ",
  #Variables affecting: gagebrth 
  "
mage -> gagebrth    
fage -> gagebrth           
mhtcm -> gagebrth    
fhtcm -> gagebrth
mwtkg -> gagebrth    
mbmi -> gagebrth    
single -> gagebrth
meducyrs -> gagebrth 
feducyrs -> gagebrth

vagbrth -> gagebrth  
hdlvry -> gagebrth

sex -> gagebrth 
brthordr -> gagebrth  
brthmon -> gagebrth 

impsan -> gagebrth 
safeh2o -> gagebrth  
trth2o -> gagebrth   
cleanck -> gagebrth  
impfloor -> gagebrth 

nchldlt5 -> gagebrth
nhh -> gagebrth
nrooms -> gagebrth

hfoodsec -> gagebrth
hhwealth -> gagebrth

arm -> gagebrth
month -> gagebrth


  ",
  #Variables affecting: vagbrth  
  "
mage -> vagbrth    
fage -> vagbrth           
mhtcm -> vagbrth    
fhtcm -> vagbrth
mwtkg -> vagbrth    
mbmi -> vagbrth    
single -> vagbrth
meducyrs -> vagbrth 
feducyrs -> vagbrth

birthwt -> vagbrth  
birthlen -> vagbrth 
gagebrth -> vagbrth 
hdlvry -> vagbrth

sex -> vagbrth 
brthordr -> vagbrth  
brthmon -> vagbrth 

impsan -> vagbrth 
safeh2o -> vagbrth  
trth2o -> vagbrth   
cleanck -> vagbrth  
impfloor -> vagbrth 

nchldlt5 -> vagbrth
nhh -> vagbrth
nrooms -> vagbrth

hfoodsec -> vagbrth
hhwealth -> vagbrth

arm -> vagbrth
month -> vagbrth

  ",
  #Variables affecting: hdlvry
  "
mage -> hdlvry    
fage -> hdlvry           
mhtcm -> hdlvry    
fhtcm -> hdlvry
mwtkg -> hdlvry    
mbmi -> hdlvry    
single -> hdlvry
meducyrs -> hdlvry 
feducyrs -> hdlvry

birthwt -> hdlvry  
birthlen -> hdlvry 
gagebrth -> hdlvry 
vagbrth -> hdlvry

sex -> hdlvry 
brthordr -> hdlvry  
brthmon -> hdlvry 

impsan -> hdlvry 
safeh2o -> hdlvry  
trth2o -> hdlvry   
cleanck -> hdlvry  
impfloor -> hdlvry 

nchldlt5 -> hdlvry
nhh -> hdlvry
nrooms -> hdlvry

hfoodsec -> hdlvry
hhwealth -> hdlvry

arm -> hdlvry
month -> hdlvry

  ",

#Birth_Chars: other, unmodifiable birth characteristics
  #Variables affecting: sex 
  "
mage -> sex    
fage -> sex              
single -> sex
meducyrs -> sex 
feducyrs -> sex

brthordr -> sex  

nchldlt5 -> sex
nhh -> sex
nrooms -> sex

hfoodsec -> sex
hhwealth -> sex

arm -> sex
month -> sex

",
  #Variables affecting: brthordr 
  "
mage -> brthordr    
fage -> brthordr           
mhtcm -> brthordr    
fhtcm -> brthordr
mwtkg -> brthordr    
mbmi -> brthordr    
single -> brthordr
meducyrs -> brthordr 
feducyrs -> brthordr

sex -> brthordr 

impsan -> brthordr 
safeh2o -> brthordr  
trth2o -> brthordr   
cleanck -> brthordr  
impfloor -> brthordr 

nchldlt5 -> brthordr
nhh -> brthordr
nrooms -> brthordr

hfoodsec -> brthordr
hhwealth -> brthordr

arm -> brthordr
month -> brthordr

  ", 
  #Variables affecting: brthmon 
    #-none
#HH_WASH: HH WASH/ construction
  #Variables affecting: impsan 
  "
mage -> impsan    
fage -> impsan           
mhtcm -> impsan    
fhtcm -> impsan
mwtkg -> impsan    
mbmi -> impsan    
single -> impsan
meducyrs -> impsan 
feducyrs -> impsan

birthwt -> impsan  
birthlen -> impsan 
gagebrth -> impsan 
vagbrth -> impsan  
hdlvry -> impsan

sex -> impsan 
brthordr -> impsan  
brthmon -> impsan 

safeh2o -> impsan  
trth2o -> impsan   
cleanck -> impsan  
impfloor -> impsan 

nchldlt5 -> impsan
nhh -> impsan
nrooms -> impsan

hfoodsec -> impsan
hhwealth -> impsan
earlybf -> impsan

arm -> impsan
month -> impsan

  ",
  #Variables affecting: safeh2o 
  "
mage -> safeh2o    
fage -> safeh2o           
mhtcm -> safeh2o    
fhtcm -> safeh2o
mwtkg -> safeh2o    
mbmi -> safeh2o    
single -> safeh2o
meducyrs -> safeh2o 
feducyrs -> safeh2o

birthwt -> safeh2o  
birthlen -> safeh2o 
gagebrth -> safeh2o 
vagbrth -> safeh2o  
hdlvry -> safeh2o

sex -> safeh2o 
brthordr -> safeh2o  
brthmon -> safeh2o 

impsan -> safeh2o  
trth2o -> safeh2o   
cleanck -> safeh2o  
impfloor -> safeh2o 

nchldlt5 -> safeh2o
nhh -> safeh2o
nrooms -> safeh2o

hfoodsec -> safeh2o
hhwealth -> safeh2o
earlybf -> safeh2o

arm -> safeh2o
month -> safeh2o

  ", 
  #Variables affecting: trth2o 
  "
mage -> trth2o    
fage -> trth2o           
mhtcm -> trth2o    
fhtcm -> trth2o
mwtkg -> trth2o    
mbmi -> trth2o    
single -> trth2o
meducyrs -> trth2o 
feducyrs -> trth2o

birthwt -> trth2o  
birthlen -> trth2o 
gagebrth -> trth2o 
vagbrth -> trth2o  
hdlvry -> trth2o

sex -> trth2o 
brthordr -> trth2o  
brthmon -> trth2o 

safeh2o -> trth2o  
impsan -> trth2o   
cleanck -> trth2o  
impfloor -> trth2o 

nchldlt5 -> trth2o
nhh -> trth2o
nrooms -> trth2o

hfoodsec -> trth2o
hhwealth -> trth2o
earlybf -> trth2o

arm -> trth2o
month -> trth2o

  ",  
  #Variables affecting: cleanck
  "
mage -> cleanck    
fage -> cleanck           
mhtcm -> cleanck    
fhtcm -> cleanck
mwtkg -> cleanck    
mbmi -> cleanck    
single -> cleanck
meducyrs -> cleanck 
feducyrs -> cleanck

birthwt -> cleanck  
birthlen -> cleanck 
gagebrth -> cleanck 
vagbrth -> cleanck  
hdlvry -> cleanck

sex -> cleanck 
brthordr -> cleanck  
brthmon -> cleanck 

safeh2o -> cleanck  
trth2o -> cleanck   
impsan -> cleanck  
impfloor -> cleanck 

nchldlt5 -> cleanck
nhh -> cleanck
nrooms -> cleanck

hfoodsec -> cleanck
hhwealth -> cleanck
earlybf -> cleanck

arm -> cleanck
month -> cleanck

  ",  
  #Variables affecting: impfloor 
"
mage -> impfloor    
fage -> impfloor           
mhtcm -> impfloor    
fhtcm -> impfloor
mwtkg -> impfloor    
mbmi -> impfloor    
single -> impfloor
meducyrs -> impfloor 
feducyrs -> impfloor

birthwt -> impfloor  
birthlen -> impfloor 
gagebrth -> impfloor 
vagbrth -> impfloor  
hdlvry -> impfloor

sex -> impfloor 
brthordr -> impfloor  
brthmon -> impfloor 

safeh2o -> impfloor  
trth2o -> impfloor   
cleanck -> impfloor  
impsan -> impfloor 

nchldlt5 -> impfloor
nhh -> impfloor
nrooms -> impfloor

hfoodsec -> impfloor
hhwealth -> impfloor
earlybf -> impfloor

arm -> impfloor
month -> impfloor

  ",

#HH_size
  #Variables affecting: nchldlt5
  "
mage -> nchldlt5    
fage -> nchldlt5           
mhtcm -> nchldlt5    
fhtcm -> nchldlt5
mwtkg -> nchldlt5    
mbmi -> nchldlt5    
single -> nchldlt5
meducyrs -> nchldlt5 
feducyrs -> nchldlt5

birthwt -> nchldlt5  
birthlen -> nchldlt5 
gagebrth -> nchldlt5 
vagbrth -> nchldlt5  
hdlvry -> nchldlt5

sex -> nchldlt5 

impsan -> nchldlt5 
safeh2o -> nchldlt5  
trth2o -> nchldlt5   
cleanck -> nchldlt5  
impfloor -> nchldlt5 

nrooms -> nchldlt5

hfoodsec -> nchldlt5
hhwealth -> nchldlt5
earlybf -> nchldlt5

arm -> nchldlt5
month -> nchldlt5

  ",
  #Variables affecting: nhh
  "
mage -> nhh    
fage -> nhh           
mhtcm -> nhh    
fhtcm -> nhh
mwtkg -> nhh    
mbmi -> nhh    
single -> nhh
meducyrs -> nhh 
feducyrs -> nhh

birthwt -> nhh  
birthlen -> nhh 
gagebrth -> nhh 
vagbrth -> nhh  
hdlvry -> nhh

sex -> nhh 

impsan -> nhh 
safeh2o -> nhh  
trth2o -> nhh   
cleanck -> nhh  
impfloor -> nhh 

nrooms -> nhh

hfoodsec -> nhh
hhwealth -> nhh
earlybf -> nhh

arm -> nhh
month -> nhh

  ",
  #Variables affecting: nrooms
"
mage -> nrooms    
fage -> nrooms           
mhtcm -> nrooms    
fhtcm -> nrooms
mwtkg -> nrooms    
mbmi -> nrooms    
single -> nrooms
meducyrs -> nrooms 
feducyrs -> nrooms

birthwt -> nrooms  
birthlen -> nrooms 
gagebrth -> nrooms 
vagbrth -> nrooms  
hdlvry -> nrooms

sex -> nrooms 
brthordr -> nrooms  
brthmon -> nrooms 

impsan -> nrooms 
safeh2o -> nrooms  
trth2o -> nrooms   
cleanck -> nrooms  
impfloor -> nrooms 

nchldlt5 -> nrooms
nhh -> nrooms

hfoodsec -> nrooms
hhwealth -> nrooms
earlybf -> nrooms

arm -> nrooms
month -> nrooms

  ",

#Variables affecting: diarrhea
"
mage -> diarrhea    
fage -> diarrhea           
mhtcm -> diarrhea    
fhtcm -> diarrhea
mwtkg -> diarrhea    
mbmi -> diarrhea    
single -> diarrhea
meducyrs -> diarrhea 
feducyrs -> diarrhea

birthwt -> diarrhea  
birthlen -> diarrhea 
gagebrth -> diarrhea 
vagbrth -> diarrhea  
hdlvry -> diarrhea

sex -> diarrhea 
brthordr -> diarrhea  
brthmon -> diarrhea 

impsan -> diarrhea 
safeh2o -> diarrhea  
trth2o -> diarrhea   
cleanck -> diarrhea  
impfloor -> diarrhea 

nchldlt5 -> diarrhea
nhh -> diarrhea
nrooms -> diarrhea

hfoodsec -> diarrhea
hhwealth -> diarrhea
earlybf -> diarrhea

arm -> diarrhea 
month -> diarrhea

  ",

#Variables affecting: BF_practice
"
mage -> BF_practice    
fage -> BF_practice           
mhtcm -> BF_practice    
fhtcm -> BF_practice
mwtkg -> BF_practice    
mbmi -> BF_practice    
single -> BF_practice
meducyrs -> BF_practice 
feducyrs -> BF_practice

birthwt -> BF_practice  
birthlen -> BF_practice 
gagebrth -> BF_practice 
vagbrth -> BF_practice  
hdlvry -> BF_practice

sex -> BF_practice 
brthordr -> BF_practice  
brthmon -> BF_practice 

impsan -> BF_practice 
safeh2o -> BF_practice  
trth2o -> BF_practice   
cleanck -> BF_practice  
impfloor -> BF_practice 

nchldlt5 -> BF_practice
nhh -> BF_practice
nrooms -> BF_practice

hfoodsec -> BF_practice
hhwealth -> BF_practice
earlybf -> BF_practice

arm -> BF_practice  
month -> BF_practice

  ",
#Variables affecting: hfoodsec
"
mage -> hfoodsec    
fage -> hfoodsec           
mhtcm -> hfoodsec    
fhtcm -> hfoodsec
mwtkg -> hfoodsec    
mbmi -> hfoodsec    
single -> hfoodsec
meducyrs -> hfoodsec 
feducyrs -> hfoodsec

birthwt -> hfoodsec  
birthlen -> hfoodsec 
gagebrth -> hfoodsec 
vagbrth -> hfoodsec  
hdlvry -> hfoodsec

sex -> hfoodsec 
brthordr -> hfoodsec  
brthmon -> hfoodsec 

impsan -> hfoodsec 
safeh2o -> hfoodsec  
trth2o -> hfoodsec   
cleanck -> hfoodsec  
impfloor -> hfoodsec 

nchldlt5 -> hfoodsec
nhh -> hfoodsec
nrooms -> hfoodsec

earlybf -> hfoodsec

hhwealth -> hfoodsec
arm -> hfoodsec
month -> hfoodsec

  ",
#Variables affecting: hhwealth
  "
mage -> hhwealth    
fage -> hhwealth           
mhtcm -> hhwealth    
fhtcm -> hhwealth
mwtkg -> hhwealth    
mbmi -> hhwealth    
single -> hhwealth
meducyrs -> hhwealth 
feducyrs -> hhwealth

birthwt -> hhwealth  
birthlen -> hhwealth 
gagebrth -> hhwealth 
vagbrth -> hhwealth  
hdlvry -> hhwealth

sex -> hhwealth 
brthordr -> hhwealth  
brthmon -> hhwealth 

impsan -> hhwealth 
safeh2o -> hhwealth  
trth2o -> hhwealth   
cleanck -> hhwealth  
impfloor -> hhwealth 

nchldlt5 -> hhwealth
nhh -> hhwealth
nrooms -> hhwealth

hfoodsec -> hhwealth
earlybf -> hhwealth

arm -> hhwealth
month -> hhwealth

  ",
#Variables affecting: enstunt
  "
mage -> enstunt    
fage -> enstunt           
mhtcm -> enstunt    
fhtcm -> enstunt
mwtkg -> enstunt    
mbmi -> enstunt    
single -> enstunt
meducyrs -> enstunt 
feducyrs -> enstunt

birthwt -> enstunt  
birthlen -> enstunt 
gagebrth -> enstunt 
vagbrth -> enstunt  
hdlvry -> enstunt

sex -> enstunt 
brthordr -> enstunt  
brthmon -> enstunt 

impsan -> enstunt 
safeh2o -> enstunt  
trth2o -> enstunt   
cleanck -> enstunt  
impfloor -> enstunt 

nchldlt5 -> enstunt
nhh -> enstunt
nrooms -> enstunt

hfoodsec -> enstunt
hhwealth -> enstunt
earlybf -> enstunt

arm -> enstunt
month -> enstunt

  ",
#Variables affecting: earlybf
  "
mage -> earlybf    
fage -> earlybf           
mhtcm -> earlybf    
fhtcm -> earlybf
mwtkg -> earlybf    
mbmi -> earlybf    
single -> earlybf
meducyrs -> earlybf 
feducyrs -> earlybf

birthwt -> earlybf  
birthlen -> earlybf 
gagebrth -> earlybf 
vagbrth -> earlybf  
hdlvry -> earlybf

sex -> earlybf 
brthordr -> earlybf  
brthmon -> earlybf 

impsan -> earlybf 
safeh2o -> earlybf  
trth2o -> earlybf   
cleanck -> earlybf  
impfloor -> earlybf 

nchldlt5 -> earlybf
nhh -> earlybf
nrooms -> earlybf

hfoodsec -> earlybf
hhwealth -> earlybf
enstunt -> earlybf

arm -> earlybf
month -> earlybf

  ",
#Variables affecting: arm
    #-none
#Variables affecting: month 
    #-none

"}")



RF_DAG <- function(d, Avar, all_exposures = c("sex", "month", "mage",   "fage",  "meducyrs",  "feducyrs", "single", 
                                              "hhwealth","hfoodsec",
                                              "mhtcm", "fhtcm","mwtkg",  "mbmi", "arm", "hdlvry", 
                                              "vagbrth", "birthwt",  "birthlen",  "gagebrth", 
                                              "brthordr",  "brthmon", "earlybf",
                                            "nchldlt5", "nhh", "nrooms",
                                            "impsan",  "safeh2o",   "trth2o",  "cleanck",  "impfloor", 
                                            "enstunt","BF_practice", "diarrhea")){
  
      parents <- str_extract_all(d, paste0("\\n(.*?) -> ",Avar))
        d2 <-d
      
      if(length(parents[[1]])>0){
        parents <- str_split(parents[[1]], " ->", simplify = T)[,1]
        parents <- str_split(parents, "\n", simplify = T)[,2]
        
        
        for(i in 1:length(parents)){
          d2 <- gsub(paste0(Avar," -> ",parents[i]),"", d2)
        }
        
        nchar(d)
        nchar(d2)
        
        
        for(i in 1:length(all_exposures)){
          for(j in 1:length(all_exposures)){
            
            test1 <- grepl(paste0(all_exposures[i]," -> ",all_exposures[j]) , d2)
            test2 <- grepl(paste0(all_exposures[j]," -> ",all_exposures[i]) , d2)
            
            if(test1 & test2){
                d2 <- gsub(paste0(all_exposures[j]," -> ",all_exposures[i]),"", d2)
            }
            #if(test1 & test2){cat(all_exposures[i],", ",all_exposures[j],"\n") }
          }  
        }
        nchar(d2)
      }
      
      g2 <- dagitty(d2)
      
      
      
      outcomes(g2) <- "Y_Stunted"
      
      exposures(g2) <- Avar
      
      #g3 <- dagitty(canonicalize(g2)$g)
      
      adj_set<-adjustmentSets( g2, Avar, "Y_Stunted", effect="total" )
            if(length(adj_set)==0){
                adj_set <- parents
            }else{
                adj_set <- gsub("\\{","",adj_set)
                adj_set <- gsub("}","",adj_set)
                adj_set <- gsub(" ","",adj_set)
                adj_set <- gsub("\"","",adj_set)
                adj_set <- gsub("c\\(","",adj_set)
                adj_set <- gsub(")","",adj_set)
                adj_set <- str_split(adj_set, ",")[[1]]
            }
      cat("Adjustment set: \n", adj_set ,"\n\n")
      
      print(ggdag_adjustment_set(g2))
      
      
      return(adj_set)
}



adj_set_list <- list()
for(i in 1:length(all_exposures)){
  adj_set_list[[i]] <- RF_DAG(d, Avar = all_exposures[i])
}

names(adj_set_list) <- all_exposures

save(adj_set_list, file="C:/Users/andre/Dropbox/HBGDki documentation/HBGDki_adj_set_list.Rdata")






```



```{r}
print(adj_set_list)

```




```{r, results="asis", echo = FALSE}

adj_set_list <- list()
for(i in 1:length(all_exposures)){
  cat("\n\n## Risk Factor: ", all_exposures[i], "\n")

  adj_set_list[[i]] <- RF_DAG(d, Avar = all_exposures[i])
}


```

