---
title: "Mortality Exploration"
author: "Andrew Mertens"
date: "October 30, 2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}

library(tidyverse)
theme_set(theme_bw())
d <- readRDS("U:/UCB-SuperLearner/Stunting rallies/mortality.rds")

d$dead2 <- d$dead
d$dead2[is.na(d$dead)] <-0
d$cohort <- paste0(d$studyid," ", d$country)



```

## Number of recorded child death by cohort (on cleaned GHAP data)


```{r, echo=F}
#Mortality information by study
knitr::kable(table(d$cohort, d$dead2))
```

Note that many studies that recorded mortality (WASH Benefits) don't have mortality data on the GHAP platfrorm (or its there in the raw data but not the harmonized datasets).


## Distribution of age of death

```{r, echo=F, message=F, warning=F}
summary(d$agedth)
ggplot(d, aes(x=agedth)) + geom_histogram() + xlim(c(0, 720)) + ylim(c(0,300))
```

Many deaths are soon after birth, but 30% come after 6 months and 43% come after 3 months.

## Distribution of age of death by cohort

```{r, echo=F, message=F, warning=F}
ggplot(d[!is.na(d$dead),], aes(x=agedth)) + geom_histogram() + xlim(c(0, 720)) + ylim(c(0,100)) + facet_wrap(~cohort)
```


Most mortality info is from ZVitambo or Jivita-3.



404 of 3822 don't have a specific age of death recorded (but we could grab the last age of anthropometry measurements to get a lower bound). 1355 have a cause of death (mostly from ZVitambo).