---
title: "Time-varying risk factor exploration"
author: "Andrew Mertens"
date: "March 14, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=F}

library(tidyverse)
load("U:/data/Compiled Datasets/CompiledLongData.Rdata")

colnames(d)


d<-d[,-c(1:2,6:15,18:23,29,33,34,37:42)]
for(i in 4:ncol(d)){
  d[,i] <- as.numeric(d[,i])
}

```



### Studies with percent days with Diarrhea

(Percent of total days under observation that the child had diarrhea during. Not time-varying-for the whole study duration.)

```{r, echo=F}
print(table(d$STUDYID[!is.na(d$PCTDIAR)]))
```

### Stratified by diarrhea flag variable

```{r, echo=F}
print(table(d$STUDYID[!is.na(d$PCTDIAR)], d$DIARFL[!is.na(d$PCTDIAR)]))
```

So it looks like for ~1/2 of studies with percent days with diarrhea information, there isn't accompanying information to tell when the diarrhea episodes occured.


###Drop diarrhea and breastfeeding variables variables that are actually subject level, rather than time-varying
```{r}
d <- subset(d, select= -c(DIARDAYS, DIAREPS, DURBRST, PCTDIAR, SUMEP,SUMDIAR, SUMDAYS))
```


```{r, include=F, warning=F, message=F}
res <- d %>% subset(., select=-c(AGEDTH,DEAD)) %>% group_by(STUDYID, SUBJID) %>% summarise_all(funs(sd), na.rm=T) %>% ungroup() %>%
  subset(., select=-c(SUBJID, AGEDAYS)) %>%group_by(STUDYID) %>% summarise_all(funs(mean), na.rm=T)
res

res_long <- reshape(as.data.frame(res), idvar="STUDYID", varying=list(2:4),  direction="long")
res_long$variable <- factor(res_long$time, labels=colnames(res)[-1])
res_long <- res_long %>% rename(mean_sd=COUGHFL) %>% filter(!is.na(mean_sd))
res_long$mean_sd[res_long$mean_sd==0] <- -0.1
res_long <- droplevels(res_long)


#Sort flag variables first
p1 <- ggplot(res_long, aes(x=variable, y=mean_sd)) +geom_bar(stat="identity") + 
      geom_hline(yintercept = 0) +
      facet_wrap(~STUDYID) + theme_bw() +
      theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Bar plot of SD's of each time varying variable
Variables:
  *  COUGHFL: Flag for child has cough at time of observation
  *  DIARFL: Flag for child has diarrhea at time of observation
  *  BFEDFL: Flag for child has breastfed on the day of observation

Barplot shows the mean of within-child standard deviations of time-varying indicators. Mean SD's of 0 indicated that the variable has no within-child variation within that study.  Mean SD's of 0 have been recoded to -0.1 for visability, so variables with no bars indicate the variable is not present in a study. 

```{r, echo=F}
print(p1)
```


## Mortality plots

### Compare DEAD flag across studies
```{r, echo=F}
print(table(d$STUDYID, d$DEAD))
```

### Children marked dead who don't have an age of death

Row: if age of death is missing
Column: indicator if the child died

```{r, echo=F}
print(table(is.na(d$AGEDTH), d$DEAD))
```


```{r, echo=F, warning=F, message=F}

df <- d %>% filter(!is.na(AGEDTH)) %>% subset(., select=c(SUBJID, AGEDAYS, STUDYID, AGEDTH, DEAD)) %>%
            group_by(STUDYID, SUBJID) %>% arrange(AGEDAYS) %>%
            mutate(errorflag= factor(as.numeric(max(AGEDAYS) > AGEDTH))) %>%
            ungroup() %>% group_by(STUDYID) %>%
            mutate(rank=rank(AGEDTH))


p2 <- ggplot(df) + 
  geom_line(aes(x=AGEDAYS, y=rank, group=SUBJID), alpha=0.2) +
  geom_point(aes(x=AGEDAYS, y=rank, group=SUBJID), alpha=0.2) +
  geom_point(aes(x=AGEDTH, y=rank, group=SUBJID, color=errorflag), shape=4, size=4) + 
  facet_wrap(~STUDYID, scales="free") +
  theme_bw() + scale_color_manual(values=c("black","red"))
```


###Plot of ages of death of children across GHAP studies with mortality information

For each study with mortality, drop children who didn't die. Rank order children by reported age of death. Y axis is rank. X axis is point and line of anthropometry observations (AGEDAYS) and X's mark the recorded age of death. X is colored red if it occurs before the age of the child at the final observation of anthropometry (AKA the age at death is in error).

```{r, echo=F}
print(p2)
```





